%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Lead Mobile Developer} % Job title
    {Vidatec Ltd} % Organization
    {Fully Remote} % Location
    {Nov. 2020 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Managing a team of 4 people, providing support \& assigning work}
        \item {Helping grow team, conducting technical interviews \& onboarding new starts}
        \item {Heavily involved in our graduate program}
        \item {Deploying multiple projects on AWS (EC2, Elastic Beanstalk, Lambda)}
        \item {Serverless projects with GraphQL - Apollo Server - API \& Next.js web app Deployed to AWS Lambda functions}
        \item {Setting up CI/CD for new projects with Bitrise \& Bitbucket pipelines}
        \item {Multiple Stripe integrations}
        \item {Running workshops with potential clients to explore their ideas and outline suitable technologies for implementation}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {React Native Developer} % Job title
    {} % Organization
    {} % Location
    {Jul. 2019 - Nov. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Software house working on a variety of apps for many clients, some being used by as many as 5 million people}
        \item {iOS \& Android apps built with React Native}
        \item {Creating iOS \& Android Native Modules where a clients 3$^{rd}$ party tool only has native SDKs (e.g. MappedIn)}
        \item {Many apps would have an accompanying CMS/API (Node.js, Knex.js, Express, Handlebars, MySQL)}
        \item {White-Labeling our exisiting products to assist in sales}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {iOS Developer} % Job title
    {Shot Scope - Golf Performance Tracker} % Organization
    {Edinburgh, Scotland} % Location
    {Jul. 2017 - Jul. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Solo developer of the native iOS app}
        \item {Required BLE to connect to, receive performance data \& upload it from all of the Shot Scope golf performance tracking wearables}
        \item {Performed initial R\&D to move mobile development to React Native}
        \item {Supported other developers in the transition to React Native}
        \item {Worked on the C\# based API hosted on Azure}
        \item {Introduced Jenkins for CI/CD}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Application Developer} % Job title
    {Agenor Technology} % Organization
    {Edinburgh, Scotland} % Location
    {Jun. 2016 - Jul. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Maintaining the Iceflo iOS app and API}
        \item {Creating the native Android version of the Iceflo app}
        \item {Creating the next-gen version of Iceflo web app (Moving from APEX to React.js with a Java API)}
        \item {Used Twillio to create chat within the next-gen Iceflo app}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {iOS Developer} % Job title
    {} % Organization
    {} % Location
    {Jun. 2015 - Jun. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Initially a 12 week summer internship, extended through my final year of university}
        \item {Developed Iceflo native iOS application}
        \item {Created API written in Java - with a PLSQL database - hosted on an Glassfish server}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Lab Tutor/Mentor} % Job title
    {The University of Dundee} % Organization
    {Dundee, Scotland} % Location
    {2014 - 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Helped 1$^{st}$, 2$^{nd}$ \& 3$^{rd}$ year students complete lab tasks \& assignments}
        \item {Assignments included: Data structures with C++, Web development with Java, Games programming with Unity/C\# \& Networking}
        \item {Tasked with providing longer 1 - 1 mentoring sessions for struggling students}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Co-Founder \& Organizer of Hackdee 2015} % Job title
    {} % Organization
    {} % Locationx
    {Mar. 2015 - Apr. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Securing sponsorship from tech companies, namely NCR \& J.P. Morgan}
        \item {Organised food, merch, challenges \& prizes from sponsors}
        \item {Ensured the 70 person event ran smoothely on the day}
      \end{cvitems}
    }

%---------------------------------------------------------


%---------------------------------------------------------


%---------------------------------------------------------
\end{cventries}
